% helpful link: https://www.youtube.com/watch?v=rvgP7IMeUn8&index=9&list=PL-p5XmQHB_JSQvW8_mhBdcwEyxdVX0c1T

\documentclass{article}

\usepackage{titlesec} % modify how sections appear
\usepackage{titling}
\usepackage[colorlinks=true, urlcolor=blue]{hyperref}
\usepackage[margin=1in]{geometry}

\titleformat{\section}
            {\Large\scshape\raggedright}  % formatting
            {}  % numbering -- \thesection adds section numbers
            {0em}  % distance between number and name
            {}% [\titlerule]  % add horizontal line below

\titleformat{\subsection}[runin]
            {\large\bfseries}
            {}
            {0.5em}
            {}


\titleformat{\subsubsection}[runin]
            {\bfseries}
            {}
            {1em}
            {}

\titlespacing{\subsubsection}
             {1em}  % left margin
             {0em}
             {0em}

\renewcommand{\maketitle}{
  \begin{center}
    {\huge\bfseries
      \theauthor}

    \vspace{1em}

    \begin{tabular}{l l}
      {\textbf{E-mail}:}  waczakj@oregonstate.edu   & {\textbf{Phone}:}  (503) 330-1280 \\
      {\textbf{Address}:} 12231 SW Pond Lane & {\textbf{Website}:}  \url{https://john-waczak.github.io/}\\
      \hspace{4.5em} King City, OR, 97224  
    \end{tabular}
    \vspace{1em}
    \par\noindent\rule{\textwidth}{1pt}
  \end{center}
}


% Defining command for entries in CV
\newcommand{\entry}[4]{
  \begin{minipage}[t]{0.15\textwidth}
    \hfill \raggedleft{\textsc{#1}}
  \end{minipage}
  \hfill\vline\hfill
  \begin{minipage}[t]{0.80\textwidth}
    \large{\textbf{#2}}

    \textit{#3}

    \vspace{0.5em}
    \footnotesize{#4}

  \end{minipage}\\ \vspace{0.25em}
}

\newcommand{\skillsentry}[2]{
  \begin{minipage}[t]{0.15\textwidth}
    \hspace{1em}
  \end{minipage}
  \hfill\vline\hfill
  \begin{minipage}[t]{0.80\textwidth}
    \large{\textbf{#1}}

    \vspace{0.5em}

    #2
  \end{minipage}\\ \vspace{0.25em}
}


\begin{document}

\title{Curriculum Vitae}
\author{John L. Waczak}
\maketitle


\section{Education}
\entry{2015-2019}
      {Oregon State University}
      {B.S. in Physics and Mathematics}
      {Thesis: Simulating the Brownian Dynamics of a Two-Dimensional Model for the Dynein Motor Protein \\
      Thesis Advisor: Dr. David Roundy}

\section{Research Experience}
\entry{2016 - Now}
      {Roundy Research Group}
      {Oregon State Physics Department}
      {I have been working with Dr. David Roundy to develop and test computational simulations for a physical model of the dynein motor protein. I regularly edit and run our simulation code in c++, I write python scripts to perform data analysis and visualization, and I present my work at our weekly group meetings. This work is the focus of my undergraduate thesis and we plan to publish the results soon thereafter.}\vspace{0.5em}\\
\entry{Jun-Aug \\ 2018}
      {Simthsonian Astrophysical Observatory Solar Physics REU}
      {Harvard-Smithsonian Center for Astrophysics}
      {Advisors: Dr. John Raymond, Dr. Chengcai Shen, Jakub Prchlik \vspace{0.25em}\\
        Using simulations for non-equilibirium ionization in coronal plasma, I analyzed the structure of spherical shock waves generated by coronal mass ejections in order to map the electron temperature and density at various positions along the shock. This involved writing Python code to interface with FORTRAN simulations, analyze FITS files from the SDO Atmospheric Imaging Assembly, and write code to fit the simulation output to observation while accounting for the round geometry.
      }

\section{Work Experience}
\entry{2015 \\ -Aug 2018}
      {Cooper Environmental Services}
      {Intern}
      {I worked for Dr. John Cooper on an x-ray fluorescence spectroscopy continuous heavy metal monitors. I developed a program in C\# to automate the quality assurance continuity check for wire harnesses before they are installed. Designed and implemented a PID control loop for setting a flow rate on a vacuum pump. I created code to make data accessible locally via a Modbus slave device.}


\section{Teaching Experience}
\entry{Spring 2018 \\ - Present}
      {Paradigms in Physics}
      {Learning Assistant}
      {I am the learning assistant for the junior year sequence of physics classes at OSU. My duties include meeting with professors daily to prepare active engagement activities, running activities during class, holding office hours, and providing feedback to professors to identify student difficulties with course material and assignments. }\vspace{0.5em}\\
\entry{Fall \& Winter 2018}
      {PH 211, 201: Introductory Physics}
      {Undergraduate Teaching Assistant}
      {I served as a laboratory TA for PH 211. I taught two sections of laboratory, held multiple office hours, graded weekly assignments, and proctored examinations.}\vspace{0.5em}\\
\entry{Winter 2017}
      {PH 199: Introduction to the Physics Major}
      {Undergraduate Teaching Assistant}
      {I served as a teaching assistant for the student organized survey of the physics major. This involved organizing lab tours, inviting guest speakers from the department, and coordinating a panel of upper division students to talk about undergrad research and the curriculum. }
\section{Community Service and Outreach}
\entry{2018}
      {OSU Discovery Days}
      {Physics Outreach}
      {I volunteer as part of the physics outreach group. This fall, we created two activities to teach classes of K-5th graders about \textit{stimulated emission} and lasers for OSU's Discovery Days event. I helped create and setup the activities and guided multiple groups through them.}\vspace{0.5em}\\
\entry{2015\\ - Now}
       {Community Outreach Inc.}
       {Lambda Chi Alpha Fraternity}
       {I volunteer for Community Outreach Inc. in Corvallis, Oregon through my fraternity.}

\section{Skills}
\skillsentry{Programming Skills}
      {Python, C++, Git, Github, Mathematica, \LaTeX, SQLite, HTML/CSS}\vspace{0.5em}\\
\skillsentry{Software}
      {Linux, Windows, MS Word, MS Excel, Google Docs}\vspace{0.5em}\\
\skillsentry{Electronics}
      {Arduino, Raspberry Pi, Soldering,  Oscilloscopes}

\section{Memberships}
\entry{2018}
      {American Geophysical Union}
      {Member\\ Presenter}
      {I presented results from my summer REU at the AGU 2018 Fall meeting in Washington, D.C.}\vspace{0.5em}\\
\entry{2017 \\ -Now}
      {$\Sigma\Pi\Sigma$ Physics Honor Society}
      {Member}
      {}\vspace{0.5em}\\
\entry{2015\\ -Now}
      {$\Lambda$XA Fraternity}
      {Vice President (2017), Fraternity Educator (2016), Member (2015)}
      {}


\end{document} 
